flowCore: A Bioconductor software package for high throughput flow cytometry data analysis \footnote{This work was supported by NIH grant EB005034 and by the Michael Smith Foundation for Health Research. RRB is an ISAC Scholar.}

### 2008-08-21 paper/manuscript.tex
title page requirement for cytometry
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@33315 bc3139a8-67e5-0310-9ffc-ced21a209358

\documentclass[12pt]{article}
\usepackage{url}
\usepackage[authoryear,round]{natbib}
\usepackage{graphicx} 
\newcommand{\Rpackage}[1]{{\textsf{#1}}}
\newcommand{\Rclass}[1]{{\textit{#1}}}

\title{flowCore: A Bioconductor software package for high throughput flow cytometry analysis}

\author{Florian Hahne*\\
  Nolwenn LeMeur*\\
  Byron Ellis\\
  Ryan R. Brinkman\\
  Perry Haaland\\
  Errol Strain\\
  Deepayan Sarkar\\
  Josef Spidlen\\
  Robert Gentleman
 }

\begin{document}

\maketitle

@@

%%Figure1 Diagram of the data structures and the basic operations
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{Figure1-flowCoreFrameWork.jpg}
\caption{\label{fig1:FrameWork}{For each experiment, the content of
    the FCS files, phenotypic and metadata are stored in a
    \Rclass{flowSet}. Each \Rclass{flowFrame} in a \Rclass{flowSet}
    corresponds to one FCS file. All basic operations (e.g.,
    compensation, transformation, gating) can be applied to either
    single \Rclass{flowFrames} or a \Rclass{flowSet} simultaneously.}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.98\textwidth]{flowQ.jpg}
\caption{\label{flowQ}%
  HTML quality assessment report generated by the flowQ package for a
  subset of data from an experiment focussing on Graft-Versus-Host
  Disease \citep{brinkman2007hcf}. Rows correspond to the samples in
  the set, columns to different quality checks.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\textwidth]{xyplot}
\caption{\label{xyplot}%
  Scatterplot matrix of a single \Rclass{flowSet} from an experiement
  focussing on immune tolerance following kidney
  transplantation. Outlines of the gating regions identified by an
  automated gating operation are added on top of the density
  representation of the data.}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage{setspace}
\usepackage{url}
\usepackage[authoryear,round]{natbib}
\usepackage{graphicx} 
\newcommand{\Rpackage}[1]{{\textsf{#1}}}
\newcommand{\Rclass}[1]{{\textit{#1}}}

\title{flowCore: A Bioconductor software package for high throughput
  flow cytometry data analysis \footnote{This work was supported by
    NIH grant EB005034 and by the Michael Smith Foundation for Health
    Research. RRB is an ISAC Scholar.}}

\author{Florian Hahne (\textit{Fred Hutchinson Cancer Research
    Center})\\
  Nolwenn LeMeur* (\textit{Fred Hutchinson Cancer Research Center})\\
  Ryan R. Brinkman (\textit{BC Cancer Research Centre})\\
  Byron Ellis (\textit{AdBrite, Inc})\\
  Perry Haaland (\textit{BD Biosciences})\\
  Deepayan Sarkar (\textit{Fred Hutchinson Cancer Research
    Center})\\
  Josef Spidlen (\textit{BC Cancer Research Centre})\\
  Errol Strain (\textit{BD Biosciences})\\
  Robert Gentleman (\textit{Fred Hutchinson Cancer Research
    Center})\\
}

\doublespacing
\begin{document}
\begin{singlespace}
\maketitle

Corresponding author:\\
\textit{
  Florian Hahne, PhD\\
  Computational Biology Program\\
  Division of Public Health Sciences\\
  Fred Hutchinson Cancer Research Center\\
  1100 Fairview Ave. N, M2-B876\\
  PO Box 19024\\
  Seattle, Washington 98109-1024\\
  phone: 206-667-3148\\
  fax: 206-667-1319\\
  fhahne@fhcrc.org
}

\end{singlespace}

@@

%%Figure1 Diagram of the data structures and the basic operations
\begin{singlespace}
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{Figure1-flowCoreFrameWork.jpg}
\caption{\label{fig1:FrameWork}{For each experiment, the content of
    the FCS files, phenotypic and metadata are stored in a
    \Rclass{flowSet}. Each \Rclass{flowFrame} in a \Rclass{flowSet}
    corresponds to one FCS file. All basic operations (e.g.,
    compensation, transformation, gating) can be applied to either
    single \Rclass{flowFrames} or a \Rclass{flowSet} simultaneously.}}
\end{figure}
\end{singlespace}

@@

\begin{singlespace}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.98\textwidth]{flowQ.jpg}
\caption{\label{flowQ}%
  HTML quality assessment report generated by the flowQ package for a
  subset of data from an experiment focussing on Graft-Versus-Host
  Disease \citep{brinkman2007hcf}. Rows correspond to the samples in
  the set, columns to different quality checks.}
\end{figure}
\end{singlespace}

@@

\begin{singlespace}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\textwidth]{xyplot}
\caption{\label{xyplot}%
  Scatterplot matrix of a single \Rclass{flowSet} from an experiement
  focussing on immune tolerance following kidney
  transplantation. Outlines of the gating regions identified by an
  automated gating operation are added on top of the density
  representation of the data.}
\end{figure}
\end{singlespace}
